5-conclusion

### 2022-07-09 5-4-era5.Rmd
fix abbreviation + more fix on markups

Figure \ref{fig:netcdf} reproduces the ERA5 data [@hersbach2020era5] row of Figure 19 in [@hersbach2020era5]. Here we explain how this would be done using cubble. The plots show that the southern polar vortex splits into two on 2002-09-26 and further splits into four on 2002-10-04. Further explanation of why this is interesting can be found in the figure source, and also [@simmons2020global], [@simmons2005ecmwf].

The ERA5 data [@hersbach2020era5] provides hourly estimates across the Earth for atmospheric, land and oceanic climate variables. The data is available in the NetCDF format from the European Centre for Medium-Range Weather Forecasts (ECMWF). It can be directly downloaded from Copernicus Climate Data Store (CDS) [@cds] website or via the package \pkg{ecmwfr} [@ecwmfr].

@@

<!--The goal of this example is to reproduce the break-up of the southern polar vortex that happened in late September and early October in 2002 in the stratosphere in the Southern Hemisphere. Therefore, we filter data corresponding to the Southern Hemisphere and restrict our analysis to four dates: 2002-09-22, 2002-09-26, 2002-09-30, and 2002-10-04.--> The downloaded netCDF data is read into \proglang{R} using the \pkg{ncdf4} package, and converted to a \code{cubble} object:

>>>>

Figure \ref{fig:netcdf} reproduces the ERA5 data row of Figure 19 in [@hersbach2020era5]. Here we explain how this would be done using in the \pkg{cubble} package. The plots show that the southern polar vortex splits into two on 2002-09-26 and further splits into four on 2002-10-04. Further explanation of why this is interesting can be found in the figure source, and also [@simmons2020global], [@simmons2005ecmwf].

The ERA5 data [@hersbach2020era5] provides hourly estimates across the Earth for atmospheric, land and oceanic climate variables. The data is available in the NetCDF format from the European Centre for Medium-Range Weather Forecasts (ECMWF). It can be directly downloaded from Copernicus Climate Data Store (CDS) [@cds] website or via the \pkg{ecmwfr} package [@ecwmfr].

@@

<!--The goal of this example is to reproduce the break-up of the southern polar vortex that happened in late September and early October in 2002 in the stratosphere in the Southern Hemisphere. Therefore, we filter data corresponding to the Southern Hemisphere and restrict our analysis to four dates: 2002-09-22, 2002-09-26, 2002-09-30, and 2002-10-04.--> The downloaded NetCDF data is read into \proglang{R} using the \pkg{ncdf4} package, and converted to a \code{cubble} object:

### 2022-07-09 5-5-interactive-graphics.Rmd
quick fixes on code markup \pkg{}, \code{}
fix abbreviation + more fix on markups

Interactive graphics can be useful because they make it possible to look at the data in a multiple of ways on-the-fly. This is especially important for spatio-temporal data, where we would like to interactively connect spatial and temporal displays. This example describes the process of using \pkg{cubble} with \pkg{crosstalk} to build an interactive display connecting a map of Australia, with ribbon plots of temperature range observed at the stations. The purpose is to explore the variation of monthly temperature range over the country. Figure \ref{fig:interactive-linking} shows three snapshots of the interactivity.

@@

```{r interactive-linking, echo = FALSE, out.width="100%", out.height="23%", fig.retina = 2, dpi = 300, fig.cap = "Exploring temperature variation using linking of a map and seasonal display. Each row is a screen dump of the process. The top row shows all locations and all temperature profiles. Selecting a particular location on the map (here Mount Elizabeth) produces the plot in the second row. The maximum and minimum temperatures are shown using a ribbon. The bottom row first selects the lowest temperature in August in the seasonal display, which highlights the corresponding station on the map (Thredbo AWS). Another  station, located in the Tasmania Island, is then selected to compare its temperature variation with Thredbo AWS.", fig.show='hold'}
knitr::include_graphics(here::here("figures/linking.png"))
knitr::include_graphics(here::here("figures/linking-north.png"))
knitr::include_graphics(here::here("figures/linking-lower.png"))
```

>>>>

Interactive graphics can be useful because they make it possible to look at the data in a multiple of ways on-the-fly. This is especially important for spatio-temporal data, where we would like to interactively connect spatial and temporal displays. This example describes the process of using the \pkg{cubble} package with the \pkg{crosstalk} package to build an interactive display connecting a map of Australia, with ribbon plots of temperature range observed at the stations. The purpose is to explore the variation of monthly temperature range over the country. Figure \ref{fig:interactive-linking} shows three snapshots of the interactivity.

@@

```{r interactive-linking, echo = FALSE, out.width="100%", out.height="23%", fig.retina = 2, dpi = 300, fig.cap = "Exploring temperature variation using linking of a map and seasonal display. Each row is a screen dump of the process. The top row shows all locations and all temperature profiles. Selecting a particular location on the map (here Mount Elizabeth) produces the plot in the second row. The maximum and minimum temperatures are shown using a ribbon. The bottom row first selects the lowest temperature in August in the seasonal display, which highlights the corresponding station on the map (Thredbo). Another  station, located in the Tasmania Island, is then selected to compare its temperature variation with the Thredbo station.", fig.show='hold'}
knitr::include_graphics(here::here("figures/linking.png"))
knitr::include_graphics(here::here("figures/linking-north.png"))
knitr::include_graphics(here::here("figures/linking-lower.png"))
```

### 2022-07-09 6-conclusion.Rmd
fix abbreviation + more fix on markups

Numerous examples are provided in the main text, appendix and package vignettes. These include creating and coercing data with mismatched names, handling hierarchical data, matching time series spatially and temporally, reproducing ERA5 plots from netCDF data. Visualization of the \code{cubble} objects can be done with interactive graphic pipelines using \pkg{crosstalk}, \pkg{plotly} and \pkg{leaflet}.

>>>>

Numerous examples are provided in the main text, appendix and package vignettes. These include creating and coercing data with mismatched names, handling hierarchical data, matching time series spatially and temporally, reproducing ERA5 plots from NetCDF data. Visualization of the \code{cubble} objects can be done with interactive graphic pipelines using \pkg{crosstalk}, \pkg{plotly} and \pkg{leaflet}.
